Is Partner Modeling Mutual?

### 2014-03-24 project-mutual-modeling.tex
Formatting, syntax

\newcommand{\M}[3]{{\mathcal{M}(#1, #2, #3)}}
\newcommand{\model}[3]{{$\mathcal{M}(#1, #2, #3)$}}
\newcommand{\Model}[3]{{$\mathcal{M}^{\circ}(#1, #2, #3)$}}

@@

\begin{equation}
p(\alpha_{t_1}(X,T) / M^{\circ}_{t_2}(A,B,X) \nearrow) \approx \frac{(M^{\circ}_{min}(A,B,X,T) -
M^{\circ}_{t_1}(A,B,X))}{cost (\alpha)}
\end{equation}

@@

Measuring \Model{A}{B}{X} is methodologically difficult. We
discriminate two steps, first to capture \model{A}{B}{X} and then to
estimate \Model{A}{B}{X}.

\begin{itemize}
    \item Capturing M (A,B,X) The simplest method is to ask A what (s)he
        believes about what B knows, feels, intends to do, etc. This raises
        obvious methodological concerns since such a question triggers a
        modeling process beyond what it would 'naturally' be. To avoid this
        bias, one can estimate mutual modeling after task completion. Then, the
        obvious drawback are memory losses and by post-hoc reconstruction. We
        have no other choice:. The first method was used in study 2 and the
        second one in the other studies.

    \item Estimating \Model{A}{B}{X}. The accuracy of
        \model{A}{B}{X} can be
        estimated in 2 ways.
        \begin{itemize}
            \item Subjective accuracy: In study 3, we compute
                \Model{A}{B}{emotions} by measuring if A describe
                B's emotions in the same way B reports her emotions 
                ($\mathcal{M}(A,B)=\mathcal{M}(B,B)$)

            \item Objective accuracy: In studies 4 and 5, w we compute
                \Model{A}{B}{knowledge} by comparing
                $\mathcal{M}^{\circ}A,B,K)$ to B's actual knowledge as it has
                measured by a test.

>>>>

\newcommand{\M}[3]{{\mathcal{M}(#1, #2, #3)}}
\newcommand{\model}[3]{{$\mathcal{M}(#1, #2, #3)$}}
\newcommand{\refmodel}[2]{{$\mathcal{M}(#1, #2)$}}
\newcommand{\Model}[3]{{$\mathcal{M}^{\circ}(#1, #2, #3)$}}

@@

\begin{equation} \label{eq:probrepair}
p(\alpha_{t_1}(X,T) / M^{\circ}_{t_2}(A,B,X) \nearrow) \approx \frac{(M^{\circ}_{min}(A,B,X,T) -
M^{\circ}_{t_1}(A,B,X))}{cost (\alpha)}
\end{equation}

@@

Each of the studies that we present in the next section have been design in such a way that, while tractable on a
robot, mutual modelling plays a key role for the task performance: the tasks
require a ``reasonably high" grounding criterion \groundingcriterion,
and all tasks are about building a solution or a representation together.

Along the same reasoning, the initial degree of common grounds \inigrounding
should be rather low (and hence the difference between initial and required
degrees rather high) in order to make mutual modelling effort more observable.
While we can exactly control the actual initial knowledge available to the
robot, estimating \inigrounding still requires special care during the design of
the experiments: as we have previously shown~\cite{lemaignan2014dynamics,
lemaignan2014cognitive} and because the interaction takes place between a human and
a robot, the initial human model of the robot can widely vary depending on
several factors like the user familiarity with technology, the effect of
novelty, the user expectations or the anthropomorphic features of the robot.

More generally, while we have explicit access to \model{R}{H}{X} (from the facts
stored in the robot belief state, as illustrated in
Table~\ref{table|beliefsfig7}), estimating \Model{R}{H}{X} also requires
\model{H}{H}{X}, which depends on the meta-cognitive competencies of the human
partner.

Conversely, measuring \Model{A}{B}{X} is methodologically difficult. We
discriminate two steps, first to capture \model{A}{B}{X} and then to
estimate \Model{A}{B}{X}.

\begin{itemize}
    \item {\bf Capturing \model{A}{B}{X}}: The simplest method is to ask $A$ what (s)he
        believes about what $B$ knows, feels, intends to do, etc. This raises
        obvious methodological concerns since such a question triggers a
        modeling process beyond what it would 'naturally' be. To avoid this
        bias, one can estimate mutual modeling after task completion. Then, the
        obvious drawback are memory losses and by post-hoc reconstruction.
        The first method was used in study 2 and the
        second one in the other studies. Another option would be to rely on external behavioural metrics like
        eye-tracking: we hypothesise for instance that the fixation time
        reflects the efforts engaged by the human to understand, hence, model,
        the others. Such an approach has however not yet been investigated in the presented studies.

    \item {\bf Estimating \Model{A}{B}{X}}: Once \model{A}{B}{X} is captured, we
        need to access the reference model \refmodel{B}{X} to estimate its
        \emph{accuracy}. Since we can only indirectly access it via what $B$
        reports (\ie \model{B}{B}{X}), accuracy can be estimated in 2 ways:

            \item Subjective accuracy: In study 3, we compute
                \Model{A}{B}{X} by measuring if $A$ describes
                $B$'s emotions in the same way $B$ reports its emotions 
                ($\M{A}{B}{X} = \M{B}{B}{X}$).

            \item Objective accuracy: In studies 4 and 5, we compute
                \Model{A}{B}{X} by comparing \Model{A}{B}{K} to $B$'s
                actual knowledge as it has measured by a test.
